Supplementary Content

### 2022-02-12 experiments/2_supplement/supplement.Rmd
updated the replication method

>>>>

```{r eval = TRUE}
all_stab <- readRDS(here("experiments/0_ss_finding/replication_method/processed_data/stab_data_replication_method.RDS"))

simlength <- 1e4
num_strains <- 2
plot_here <- all_stab %>%
  filter(simlength == simlength)
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(simlength,
                                                           " sim. length,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ") 
p1 + p2
